---
title: "STA 522 Project 1 (Survey of Textbooks)"
author: "Arpita Mandan, Daniel Truver"
date: "2/5/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
load("surveyData.Rdata")
```

##### (1) Sampling Design

-Stratify by department `r unique(surveyData$department)`

-SRS within department

-within stratum sample size chosen by optimum allocation formula

-total nuber of cases: 54. used optimal allocation formula with n = 50, then added one to all cases that rounded to 0, for a total of 54

- why 54? seems reasonable considering there are 358 total courses in our frame

##### (2) Data Collection

-took courses with names directly attacked to the natural sciences listed on https://trinity.duke.edu/natural-sciences

-did not include departments with course numbers all about 700

-did not include engineering of any kind

-basic test was "did department name include the words biology, chemistry, computer science, evolutionary antrhopoly, mathematics, physics, psychology, neuroscience, or statistical science?" 
--i.e. "info science" not included, "biochemistry and neurobiology included"
--Could be a source of selection bias, but had to make the call somewhere

-sampling frame obtained via web scraping, see code at the end. data obtained manually due to difficulty of scraping when section numbers can be 01 or 001

##### (3) Survey Values

```{r loadInData}
load("surveyData.Rdata")
load("classes.Rdata")
library(survey)
```

```{r makeWeightsAndFPC}
fpcvar = c() #bad practice, but data small enough to allow for it
wtvar = c()

N_h = c() #construct number of classes per stratum
for (school in names(classes.df)){
  N_h[school] = sum(classes.df[,school] != "")
}
n = 50
N = sum(N_h)
n_h = round(n* (N_h/N) )
n_h[n_h == 0] = 1
n = sum(n_h)

for (dep in names(n_h)){
  fpcvar = c(fpcvar, rep(N_h[dep], n_h[dep])) # grow vector of fpc's
  wtvar = c(wtvar, rep(N_h[dep]/n_h[dep], n_h[dep]))
}

des = svydesign(~1, strata = ~department, weights = wtvar, fpc = fpcvar, data = surveyData)
```

- need all MGM and BIOCHEM

- report required values here

##### (4) Discussion

-this section may be unnecessary.